\documentclass[margin,line]{res}


\usepackage{hyperref}
\hypersetup{
   colorlinks,
   citecolor=black,
   filecolor=black,
   linkcolor=black,
   urlcolor=blue
}

\usepackage{url}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

%if using pdflatex:
\setlength{\pdfpagewidth}{\paperwidth}
\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{Enes Kemal Ergin \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{4in}}
11929 W Airport Blvd         & {\it GitHub:}  \href{https://github.com/eneskemalergin}{eneskemalergin} \\            
North American University    & {\it E-mail:}  \href{mailto:eneskemalergin@gmail.com}{eneskemalergin@gmail.com}\\       
Stafford, Texas 77477        & {\it Blog:}  \href{eneskemalergin.github.io}{eneskemalergin.github.io} \\     
\end{tabular}


\section{\sc Research Interests}
Deep learning applications in genomics and epigenomics, cancer genomics, next-generation sequencing analysis, systems biology, machine learning applications

\section{\sc Education}

% Uncomment for PhD
%{\bf Stanford School of Medicine}, Stanford, California USA\\
%{\em Biomedical Informatics} 
%\begin{list1}
%\item[] Ph.D. Candidate, Biomedical Informatics, September 2017 (expected
%  graduation date: May 2022)
%\begin{list2}
%\vspace*{.05in}
%\item Dissertation Topic:  ``Nonstationary Covariance Models for
%  Spatial Data and Regression Problems'' 
%\item Dissertation Topic:  ``Hierarchical Models for Multiple Ratings
%  in Performance-Based\\ \hspace*{1.23in} Student Assessments.'' 
%
%\item Advisor:  Andshul Kundaje
%\end{list2}
%\end{list1}

{\bf North American University (NAU)}, Stafford, Texas USA\\
\vspace*{-.1in}
\begin{list1}
\item[] B.S., Computer Science,  May, 2017
\end{list1}


\section{\sc Honors and Awards} 


North American University: Exceptional Merit Scholarship, 2012-2017

\vspace*{-2.5mm}
North American University: Graduated Magna Cum Laude, Honors in Computer Science, 2017

\vspace*{-2.5mm}
North American University: Outstanding Student of the Year, 2015

\vspace*{-2.5mm}
North American University: President's Honor Roll , 2015-2017


\section{\sc Research Experience}

{\bf Visiting Researcher}

\vspace{-.3cm}
{\em Harvard Medical School} \hfill {\bf November, 2015 - September, 2016}\\
\vspace{-.3cm}
\begin{list2}
\item Research: Predicting the determinant of alternative splicing of RNA transcription
\begin{list2}
\item Worked with Lua/Torch, Python Pandas, Numpy, Matplotlib
\item Developed a deep learning model, convolutional neural network model using Torch7 
\end{list2}
\item Research: Predicting transcription factor binding sites across cell types
\begin{list2}
\item Attended a ENCODE-DREAM competition: (\href{https://www.synapse.org/#!Synapse:syn6131484}{Link})
\item Worked with Linux terminal tools, Python (Tensorflow, Pandas, Numpy, Matplotlib)
\item Implemented a deep learning model, multi-task convolutional neural network model using Tensorflow
\end{list2}
\end{list2}

{\bf Undergraduate Research Assistant}

\vspace{-.3cm}
{\em North American University} \hfill {\bf September, 2015 - present}\\
Lead student of Bioinformatics Lab at NAU. Closely followed 4 students and mentored them.\\
Created open source bioinformatics curriculum with Open Source Society in GitHub.

{\em Yeditepe University} \hfill {\bf August, 2014 - May, 2015}\\
Worked remotely as an genomic data scientist and investigated data from NCBI PubMed database. Utilized virtual docking software to determine the best possible inhibitor for specific molecule.  
%\begin{list2}
%\item 
%\end{list2}

{\em Texas Institute of Education and Research (TIBER)} \hfill {\bf September, 2014 - April, 2015}\\
Worked as an experimental biologist on sinusitis bacteria. 
Designed experiments by preparing agar solutions, and bacteria culture.
Only worked on wet-lab experiments.


\section{\sc Teaching Experience}
{\bf North American University}, Stafford, TX USA

\vspace{-.3cm}
{\em Teaching Assistant} \hfill {\bf September 2015 - Present}\\
Co-taught 3 undergraduate level courses for computer science department. Prepared the lab sessions and extra sessions on Git/GitHub, Rapid Python Programming, and Ipython/Jupyter. Shared responsibility for lectures, exams, homework assignments, and  grades.
\vspace*{.05in}  
\begin{list2}
\item COMP 3317 Algorithms, Fall 2015, 2016.
\item COMP 3320 Programming Languates, Fall 2016.
\item COMP 3322 Software Engineering, Fall 2016.
\end{list2}

\vspace{-.3cm}
{\em Instructor} \hfill {\bf February - April 2015}\\
Taught Basic Python programming to 35 people including students, faculty, and staff of NAU, which was a first ever course taught purely by a student in NAU history. (\href{https://github.com/NAU-Python-Class/Py101-Spring-15}{Link})


\section{\sc Publications}
Kocabas, F., Ergin, E.K. 2016. Identification of small molecule binding pocket for inhibition of Crimean-Congo hemorrhagic fever virus OTU protease. Turkish Journal of Biology, 40:239-249.



%\section{\sc Papers in preparation}
%
% Kocabas, F., Ergin, E.K. 2016. Identification of small molecule binding pocket for inhibition of Crimean-Congo hemorrhagic fever virus OTU protease. Turkish Journal of Biology, 40:239-249.

%\section{\sc Conference Presentations}
%
% Kocabas, F., Ergin, E.K. 2016. Identification of small molecule binding pocket for inhibition of Crimean-Congo hemorrhagic fever virus OTU protease. Turkish Journal of Biology, 40:239-249.



\section{\sc Projects}
{\bf Open Source Bioinformatics Curriculum} \hfill {\bf June  2016}\\
4 year worth, open source source bioinformatics curriculum developed by my lab and contributed by open source society and other contributers around the world. (\href{https://github.com/open-source-society/bioinformatics}{Link})

{\bf Scholar Development Center} \hfill {\bf February  2016}\\
Created a non-profit community based organization under the Raindrop Foundation to help Turkish undergraduate students around Texas to achieve their dreams in academia or industry. 

{\bf Essential Algorithms} \hfill {\bf September 2014}\\
Put together a repository which contains algorithms from A Practical Approach to Computer Algorithms by Rod Stephens, Number Theory, and other useful algorithms written in Python. (\href{https://github.com/eneskemalergin/Essential_Algorithms}{Link})

\section{\sc Extracurricular Activities}
\begin{list2}
\item NAU Kazakh Student Association, {\em Club Advisor} \hfill {\bf September 2016 - Present} 
\item ISCB (International society of computational biology), {\em Member} \hfill {\bf August, 2016- Present}
\item NAU Future Leaders Club, {\em Founder and Director} \hfill {\bf April, 2015 - Present}
\item Student Government, {\em VP of Unity and Social Justice} \hfill  {\bf September 2014 - Present}
\item ACM (Association for Computing Machinery), {\em Member} \hfill  {\bf February 2013 - Present}
\item NAU ACM, {\em Member} \hfill {\bf September 2013 - Present}
\item NAU ACM, {\em Vice President} \hfill  {\bf September 2015 - May 2016}
\item NAU ACM, {\em Secretary} \hfill  {\bf February 2013 - September 2014}
\end{list2}

\section{\sc Technical Skills} 
\begin{list2}
\item {\bf Languages:}  Python(Pandas, Numpy, H5py, Tensorflow, Biopython, Scikit-learn), R, Java, \LaTeX, C/C++, Javascript, HTML, CSS
\item {\bf Database Systems:} SQL, MySQL, MongoDB
\item {\bf Operating Systems:}  Unix/Linux, MacOS, Windows.
\end{list2}

\section{\sc References} 
**References upon to a request



\end{resume}
\end{document}




